% Orange: Phase 2 Technical Implementation Report
% Prepared by Claude Opus 4.7 — automated technical author
% Date: 2026-05-12

\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}

\geometry{
  top=2.5cm, bottom=2.5cm,
  left=3cm, right=3cm
}

% Colour palette (matches Phase 1 report)
\definecolor{deepforest}{RGB}{34, 85, 55}
\definecolor{mossgreen}{RGB}{90, 140, 90}
\definecolor{warmamber}{RGB}{210, 140, 50}
\definecolor{sunlitgold}{RGB}{220, 170, 60}
\definecolor{softcream}{RGB}{252, 248, 238}
\definecolor{critred}{RGB}{180, 30, 30}
\definecolor{highoran}{RGB}{210, 100, 20}
\definecolor{medyell}{RGB}{180, 150, 10}
\definecolor{lowblue}{RGB}{50, 100, 170}
\definecolor{passgre}{RGB}{30, 130, 60}
\definecolor{codegrey}{RGB}{245, 245, 245}

\hypersetup{
  colorlinks=true,
  linkcolor=deepforest,
  urlcolor=mossgreen,
  citecolor=mossgreen,
  pdftitle={Orange: Phase 2 Technical Implementation Report},
  pdfauthor={Technical Author},
}

\lstset{
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{codegrey},
  frame=single,
  breaklines=true,
  columns=fullflexible,
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{mossgreen}{\textit{Orange}}}
\fancyhead[R]{\small Phase 2 Technical Implementation Report}
\fancyfoot[C]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\titleformat{\section}
  {\large\bfseries\color{deepforest}}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalsize\bfseries\color{mossgreen}}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\normalsize\itshape\color{deepforest}}{\thesubsubsection}{1em}{}

% Status badge helpers
\newcommand{\statuspass}{\textcolor{passgre}{\textbf{PASS}}}
\newcommand{\statusfail}{\textcolor{critred}{\textbf{FAIL}}}
\newcommand{\statuswarn}{\textcolor{medyell}{\textbf{WARN}}}
\newcommand{\statusna}{\textcolor{gray}{\textbf{N/A}}}
\newcommand{\sevCrit}{\textcolor{critred}{\textbf{CRITICAL}}}
\newcommand{\sevHigh}{\textcolor{highoran}{\textbf{HIGH}}}
\newcommand{\sevMed}{\textcolor{medyell}{\textbf{MEDIUM}}}
\newcommand{\sevLow}{\textcolor{lowblue}{\textbf{LOW}}}
\newcommand{\sevFixed}{\textcolor{passgre}{\textbf{FIXED}}}

% ============================================================================

\begin{document}

\begin{titlepage}
  \centering
  \vspace*{2cm}
  {\Huge\bfseries\color{deepforest} Orange\par}
  \vspace{0.5cm}
  {\Large\color{mossgreen} Phase 2 Technical Implementation Report\par}
  \vspace{0.3cm}
  {\large\itshape Episode 2 --- Sunlit Waterfall\par}
  \vspace{0.2cm}
  {\normalsize\itshape Prompts P31\,--\,P42 and Final Post-Audit Fixes\par}
  \vspace{2cm}
  \rule{0.6\linewidth}{1pt}\par
  \vspace{1cm}
  \begin{tabular}{ll}
    \textbf{Prepared by:}     & Automated Technical Author (Claude Opus 4.7) \\
    \textbf{Date:}            & 2026-05-12 \\
    \textbf{Engine:}          & Godot 4.3 (Compatibility renderer) \\
    \textbf{Language:}        & GDScript only \\
    \textbf{Repository:}      & \texttt{/Orange} (main branch) \\
    \textbf{Phase 1 status:}  & Complete (see Phase 1 report) \\
    \textbf{Phase 2 status:}  & Implemented, audited, post-audit fixes applied \\
    \textbf{Milestone:}       & \textcolor{passgre}{\textbf{PASS}} (Episode 2 complete) \\
  \end{tabular}
  \vspace{2cm}
  \rule{0.6\linewidth}{0.4pt}\par
  \vspace{0.5cm}
  {\small\itshape This report documents the implementation of Phase 2 (Episode 2:
  Sunlit Waterfall) and the verification of the four post-audit fixes that
  followed the Phase 2 QA pass. The report is generated from a static
  inspection of the repository; it does not substitute for runtime
  playtesting or a web export smoke test.\par}
\end{titlepage}

% ============================================================================
\tableofcontents
\newpage

% ============================================================================
\section{Executive Summary}

Phase 2 extends the \textit{Orange} prototype from the Episode 2 sunlit bridge
into a complete Episode 2 (\textit{Sunlit Waterfall}). The phase is built
strictly on the architecture established in Phase 1: no new autoloads, no new
global signals, no new folders outside the additions in
\texttt{phase2\_prompts.md} \S5.

Phase 2 delivers:

\begin{itemize}[nosep]
  \item Four new Episode 2 zones (\texttt{ep2.zone\_1}\,--\,\texttt{ep2.zone\_4}).
  \item Four new Episode 2 puzzles (Sun Reflection, Water Flow Path,
        Mist Symbol, Rock Water).
  \item Four Mixed Compass fragment rewards filling \texttt{MiniFrame} slots 0\,--\,3.
  \item The Mixed Compass completion moment and the Episode 2 end card
        (\texttt{Ep2EndCard}).
  \item A live bridge\,$\to$\,Episode 2 transition through
        \texttt{EpisodeController}, replacing the Phase 1 prototype end card.
  \item Targeted edits to \texttt{globals/constants.gd},
        \texttt{globals/episode\_controller.gd}, and
        \texttt{episodes/zone.gd} for episode detection and routing.
\end{itemize}

A Phase 2 QA audit identified four issues. All four were resolved through
targeted fix prompts and have been verified in the current repository:

\begin{center}
\begin{tabular}{lccc}
\toprule
\textbf{Category} & \textbf{Found} & \textbf{Fixed} & \textbf{Remaining} \\
\midrule
Critical (Episode 2 unplayable) & 2 & 2 & 0 \\
Medium (architecture / data)    & 1 & 1 & 0 \\
Low (canonical text)            & 1 & 1 & 0 \\
\midrule
\textbf{Total}                  & \textbf{4} & \textbf{4} & \textbf{0} \\
\bottomrule
\end{tabular}
\end{center}

Static verification confirms the Episode 2 reward chain is now intact:
puzzle solve $\to$ fragment reveal $\to$ manual collection $\to$ MiniFrame
slot fill $\to$ save $\to$ Mixed Compass completion $\to$ Ep2EndCard.

\textbf{Phase 2 is ready for a final runtime smoke test and a web export
validation pass.}

% ============================================================================
\section{Phase 2 Scope}

\subsection{Implementation Prompts P31\,--\,P42}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Prompt} & \textbf{Module} \\
\midrule
P31 & Episode 2 constants (puzzle, fragment, zone IDs) \\
P32 & Episode 2 JSON data (dialogue, hints, floating labels) \\
P33 & Episode 2 puzzle resource definitions (\texttt{.tres}) \\
P34 & Episode 2 zone scenes (four shells) \\
P35 & Core routing wiring (EpisodeController, zone.gd) \\
P36 & Bridge\,$\to$\,Episode 2 live transition; PrototypeEndCard removal \\
P37 & Sun Reflection puzzle (zone 1) \\
P38 & Water Flow Path puzzle (zone 2) \\
P39 & Mist Symbol puzzle (zone 3) \\
P40 & Rock Water puzzle (zone 4) \\
P41 & Mixed Compass completion + Ep2EndCard \\
P42 & Final Episode 2 integration pass \\
\bottomrule
\end{tabular}
\end{center}

\subsection{In Scope}

\begin{itemize}[nosep]
  \item Four ep2 zones, puzzles, and fragment rewards.
  \item Three new JSON files under \texttt{data/}.
  \item Mixed Compass completion trigger in zone 4 and Ep2EndCard.
  \item Surgical updates to constants, EpisodeController, and zone.gd.
  \item Removal of \texttt{PrototypeEndCard} from the bridge zone scene.
\end{itemize}

\subsection{Out of Scope}

Episode 3, the Teleportation Door, dialogue trees, multi-tier hints, inventory
menus, settings menus, save slots, combat, multiplayer, and procedural
generation are explicitly out of scope and remain unimplemented.

% ============================================================================
\section{Architecture Continuity from Phase 1}

Phase 2 introduces no new architecture. All Phase 2 systems compose existing
Phase 1 modules.

\begin{center}
\begin{tabular}{p{0.36\linewidth} p{0.56\linewidth}}
\toprule
\textbf{Phase 1 contract} & \textbf{Phase 2 reuse} \\
\midrule
Six autoloads in fixed order             & Unchanged. No new autoloads. \\
Ten typed \texttt{EventBus} signals      & Unchanged. No new signals. \\
\texttt{EpisodeController} = sole scene router & Extended with ep2 zone paths and the bridge\,$\to$\,ep2 \texttt{key\_item\_used} handler. Still the only module that calls \texttt{change\_scene\_to\_file}. \\
\texttt{PuzzleBase} lifecycle (INACTIVE\,$\to$\,ACTIVE\,$\to$\,SOLVED) & Each ep2 puzzle subclasses \texttt{PuzzleBase}; uses \texttt{start\_puzzle()}, \texttt{mark\_solved()}, and \texttt{\_on\_already\_solved()} unchanged. \\
\texttt{InteractionManager.action\_dispatched} else-branch & Ep2 sub-interactable IDs (e.g.\ \texttt{ep2.sun\_reflection.stone\_1}) fall through to this branch; \texttt{\_dispatch\_action} is untouched. \\
\texttt{FragmentPickup} + \texttt{FragmentReward} & Reused as-is. Each ep2 zone instances a \texttt{FragmentPickup} with an inline \texttt{FragmentReward} sub-resource. \\
\texttt{MiniFrame} (slot-based fill)     & Reused. The Mixed Compass uses slots 0\,--\,3. \\
\texttt{KeyItemInventory}                & Reused. The Mixed Compass is granted by \texttt{MiniFrame} firing \texttt{key\_item\_completed}. \\
\texttt{SaveSystem} (single writer)      & Reused. Save fires on each fragment collection; never per-frame. \\
\texttt{HUD}, \texttt{ActionButton}, \texttt{DialogueBox}, \texttt{HintButton} & Reused unchanged. Hint and dialogue JSON for ep2 are merged via existing array-of-paths loaders. \\
\bottomrule
\end{tabular}
\end{center}

% ============================================================================
\section{Implemented File Structure}

Phase 2 adds the following files; folder structure matches
\texttt{phase2\_prompts.md} \S5.

\begin{lstlisting}
res://
  episodes/
    episode_2/
      zones/
        zone_1_waterfall_entry.tscn
        zone_2_upper_stream.tscn
        zone_3_mist_pool.tscn
        zone_4_rock_face.tscn
      puzzles/
        sun_reflection/
          sun_reflection_puzzle.tscn
          sun_reflection_puzzle.gd
        water_flow_path/
          water_flow_path_puzzle.tscn
          water_flow_path_puzzle.gd
        mist_symbol/
          mist_symbol_puzzle.tscn
          mist_symbol_puzzle.gd
        rock_water/
          rock_water_puzzle.tscn
          rock_water_puzzle.gd
      definitions/
        puzzle_sun_reflection.tres
        puzzle_water_flow.tres
        puzzle_mist_symbol.tres
        puzzle_rock_water.tres
  data/
    dialogue/episode_2.json
    hints/episode_2.json
    floating_labels/episode_2.json
  ui/
    ep2_end_card.tscn
    ep2_end_card.gd
\end{lstlisting}

Files surgically edited (no rewrites): \texttt{globals/constants.gd},
\texttt{globals/episode\_controller.gd}, \texttt{episodes/zone.gd},
\texttt{ui/hint\_button.gd} (paths array), \texttt{ui/dialogue\_box.gd}
(paths array), \texttt{interaction/interaction\_manager.gd} (paths array),
\texttt{episodes/episode\_2\_bridge/zones/zone\_sunlit\_clearing.tscn}
(removed \texttt{EndCardLayer} and \texttt{PrototypeEndCard} nodes).

% ============================================================================
\section{Constants and Identifiers}

All Episode 2 identifiers are declared as typed \texttt{StringName} constants
in \texttt{globals/constants.gd}. No string literals are used in the puzzle
or routing code paths.

\subsection{Puzzle IDs}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Constant} & \textbf{Value} \\
\midrule
\texttt{PUZZLE\_SUN\_REFLECTION} & \texttt{\&"ep2.sun\_reflection"} \\
\texttt{PUZZLE\_WATER\_FLOW}     & \texttt{\&"ep2.water\_flow"} \\
\texttt{PUZZLE\_MIST\_SYMBOL}    & \texttt{\&"ep2.mist\_symbol"} \\
\texttt{PUZZLE\_ROCK\_WATER}     & \texttt{\&"ep2.rock\_water"} \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Fragment IDs}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Constant} & \textbf{Value} \\
\midrule
\texttt{FRAG\_COMPASS\_1} & \texttt{\&"ep2.compass.frag\_1"} \\
\texttt{FRAG\_COMPASS\_2} & \texttt{\&"ep2.compass.frag\_2"} \\
\texttt{FRAG\_COMPASS\_3} & \texttt{\&"ep2.compass.frag\_3"} \\
\texttt{FRAG\_COMPASS\_4} & \texttt{\&"ep2.compass.frag\_4"} \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Zone IDs}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Constant} & \textbf{Value} \\
\midrule
\texttt{ZONE\_EP2\_1} & \texttt{\&"ep2.zone\_1"} \\
\texttt{ZONE\_EP2\_2} & \texttt{\&"ep2.zone\_2"} \\
\texttt{ZONE\_EP2\_3} & \texttt{\&"ep2.zone\_3"} \\
\texttt{ZONE\_EP2\_4} & \texttt{\&"ep2.zone\_4"} \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Episode ID and Prefix Safety}

The Episode 2 episode identifier is \texttt{\&"ep2"}. It is distinct from
\texttt{\&"ep2bridge"}. All zone IDs use the prefix \texttt{"ep2."} (with a
dot) so that string-prefix tests do not collide with \texttt{"ep2bridge"}.
The check order in both \texttt{EpisodeController.\_on\_node\_added} and
\texttt{zone.gd.\_ready} is:

\begin{lstlisting}
if zid.begins_with("ep2bridge"):
    set_episode(&"ep2bridge")
elif zid.begins_with("ep2."):
    set_episode(&"ep2")
elif zid.begins_with("ep1"):
    set_episode(&"ep1")
\end{lstlisting}

This order is load-bearing: testing \texttt{"ep2."} before \texttt{"ep2bridge"}
would misclassify the bridge as Episode 2.

% ============================================================================
\section{Data Layer}

Three new JSON files were added under \texttt{data/} for Episode 2 content.
JSON remains text-only; no gameplay state is stored in JSON.

\subsection{Dialogue (\texttt{data/dialogue/episode\_2.json})}

Fourteen keyed entries: per-puzzle \texttt{\_intro}, \texttt{\_wrong}, and
\texttt{\_solved} lines for each of the four puzzles; a zone entry line
(\texttt{ep2.entry}); and the Mixed Compass completion line
(\texttt{ep2.compass\_completed}). Each entry has an \texttt{orange}
fictional-language string and an \texttt{english} translation.

\subsection{Hints (\texttt{data/hints/episode\_2.json})}

Four plain-string hint entries keyed by puzzle ID. Hints are one-level only,
consistent with the Phase 1 \texttt{HintButton} contract.

\subsection{Floating Labels (\texttt{data/floating\_labels/episode\_2.json})}

Fifteen entries: three reflective stones, three flow channels and one water
gate, four mist panels, and four erosion marks. Labels are short, neutral
nouns intended to be displayed by \texttt{InteractionManager} on tap.

\subsection{Array-Merge Loader Pattern}

All three loaders (\texttt{DialogueBox}, \texttt{HintButton},
\texttt{InteractionManager}) iterate an internal \texttt{Array[String]} of
JSON paths and merge the parsed dictionaries with the existing data. Missing
files are silently skipped. The Episode 2 JSON paths were appended to each
loader's path array; no logic was rewritten.

\begin{lstlisting}
const _HINT_PATHS: Array[String] = [
    "res://data/hints/episode_1.json",
    "res://data/hints/episode_2_bridge.json",
    "res://data/hints/episode_2.json",
]
\end{lstlisting}

% ============================================================================
\section{Puzzle Definition Resources}

Each Episode 2 puzzle is described by a \texttt{PuzzleDefinition} resource
that carries an inline \texttt{FragmentReward} sub-resource. All four
\texttt{.tres} files declare \texttt{episode\_id = \&"ep2"} and
\texttt{key\_item\_id = \&"key.mixed\_compass"}.

\begin{center}
\begin{longtable}{p{0.16\linewidth} p{0.20\linewidth} p{0.30\linewidth} p{0.10\linewidth} p{0.10\linewidth}}
\toprule
\textbf{Puzzle} & \textbf{Puzzle ID} & \textbf{Definition Path} & \textbf{Frag.} & \textbf{Slot} \\
\midrule
\endfirsthead
\bottomrule
\endlastfoot

Sun Reflection &
\texttt{ep2.sun\_reflection} &
\texttt{episode\_2/definitions/} \texttt{puzzle\_sun\_reflection.tres} &
frag\_1 & 0 \\

Water Flow Path &
\texttt{ep2.water\_flow} &
\texttt{episode\_2/definitions/} \texttt{puzzle\_water\_flow.tres} &
frag\_2 & 1 \\

Mist Symbol &
\texttt{ep2.mist\_symbol} &
\texttt{episode\_2/definitions/} \texttt{puzzle\_mist\_symbol.tres} &
frag\_3 & 2 \\

Rock Water &
\texttt{ep2.rock\_water} &
\texttt{episode\_2/definitions/} \texttt{puzzle\_rock\_water.tres} &
frag\_4 & 3 \\

\end{longtable}
\end{center}

% ============================================================================
\section{Zone Implementation}

Each Episode 2 zone follows the Episode 1 template: \texttt{Node2D} root
with \texttt{episodes/zone.gd}, a \texttt{Background} placeholder, a 2560\,$\times$\,1440
\texttt{WalkableArea}, an \texttt{Interactables} group, the standard UI bundle
(HUD, ActionButton, DialogueBox, HintButton, InteractionManager), and an
\texttt{OrangeCharacter} with a \texttt{FollowCamera}. Zones 1\,--\,3 carry a
\texttt{ZoneExit} pointing to the next zone; zone 4 carries the compass
completion trigger and the \texttt{Ep2EndCard} instead.

\begin{center}
\begin{longtable}{p{0.07\linewidth} p{0.13\linewidth} p{0.27\linewidth} p{0.16\linewidth} p{0.07\linewidth} p{0.13\linewidth}}
\toprule
\textbf{Zone} & \textbf{Zone ID} & \textbf{Scene Path} & \textbf{Puzzle} & \textbf{Frag.} & \textbf{Exit Target} \\
\midrule
\endfirsthead
\bottomrule
\endlastfoot

1 & \texttt{ep2.zone\_1} & \texttt{episode\_2/zones/} \texttt{zone\_1\_waterfall\_entry.tscn}
  & Sun Reflection  & frag\_1 & \texttt{ep2.zone\_2} \\

2 & \texttt{ep2.zone\_2} & \texttt{episode\_2/zones/} \texttt{zone\_2\_upper\_stream.tscn}
  & Water Flow Path & frag\_2 & \texttt{ep2.zone\_3} \\

3 & \texttt{ep2.zone\_3} & \texttt{episode\_2/zones/} \texttt{zone\_3\_mist\_pool.tscn}
  & Mist Symbol     & frag\_3 & \texttt{ep2.zone\_4} \\

4 & \texttt{ep2.zone\_4} & \texttt{episode\_2/zones/} \texttt{zone\_4\_rock\_face.tscn}
  & Rock Water      & frag\_4 & (none --- Ep2EndCard) \\

\end{longtable}
\end{center}

Every zone instances a \texttt{FragmentPickup} node under \texttt{Interactables}
with an inline \texttt{FragmentReward} sub-resource matching the zone's puzzle.
Each zone scene also declares the connection
\texttt{InteractionManager.action\_dispatched} $\to$
\texttt{Interactables/FragmentPickup.\_on\_action\_dispatched}, so the pickup
receives the ``Collect'' action when the player taps it after the puzzle solves.

Zone 4 additionally contains:

\begin{itemize}[nosep]
  \item a \texttt{CompletionTrigger} node (inline script) that hides
        \texttt{ActionButton} on \texttt{key\_item\_completed(\&"key.mixed\_compass")};
  \item an \texttt{Ep2CompletionLayer} (\texttt{CanvasLayer}, \texttt{layer = 64})
        hosting the \texttt{Ep2EndCard}.
\end{itemize}

% ============================================================================
\section{Puzzle Implementation Details}

Each Episode 2 puzzle is a \texttt{Node2D} scene whose root script subclasses
\texttt{PuzzleBase}. The puzzle scene contains its sub-interactables as
\texttt{Area2D} children (each carrying \texttt{interaction/interactable.gd}).
None of the ep2 puzzle roots is itself an \texttt{Interactable}; the puzzles
auto-start when the zone loads. After the BUG-002 fix, the auto-start is
deferred so that listeners later in the zone's child order
(\texttt{HintButton}, \texttt{DialogueBox}) connect to \texttt{puzzle\_started}
and \texttt{dialogue\_requested} before the signals fire.

The shared auto-start pattern, present in all four puzzles, is:

\begin{lstlisting}
func _ready() -> void:
    super()
    if _state == State.INACTIVE:
        call_deferred("_deferred_start")
    elif _state == State.ACTIVE:
        _connect_manager()

func _deferred_start() -> void:
    if _state != State.INACTIVE:
        return
    start_puzzle()
    _connect_manager()
\end{lstlisting}

\subsection{Sun Reflection (zone 1)}

\begin{itemize}[nosep]
  \item Scene: \texttt{episodes/episode\_2/puzzles/sun\_reflection/} \texttt{sun\_reflection\_puzzle.tscn}
  \item Script: same folder, \texttt{sun\_reflection\_puzzle.gd}
  \item Sub-interactables: \texttt{Stone1}, \texttt{Stone2}, \texttt{Stone3}
        with IDs \texttt{ep2.sun\_reflection.stone\_\{1,2,3\}}
  \item Action label: ``Rotate''
  \item Exports: \texttt{correct\_rotation\_stone1/2/3 : int} (defaults 2, 1, 3)
  \item Mechanic: each tap rotates the stone by 90$^\circ$ (\texttt{rotation\_step}
        wraps mod 4); after every rotate, the puzzle checks all three rotations
        against their correct values.
  \item Solve condition: all three rotations equal their exported correct values.
  \item Wrong-answer behavior: none --- no dialogue, no state reset; the player
        keeps rotating.
  \item Fragment reward: \texttt{ep2.compass.frag\_1}, MiniFrame slot 0.
\end{itemize}

\subsection{Water Flow Path (zone 2)}

\begin{itemize}[nosep]
  \item Scene: \texttt{episodes/episode\_2/puzzles/water\_flow\_path/} \texttt{water\_flow\_path\_puzzle.tscn}
  \item Script: same folder, \texttt{water\_flow\_path\_puzzle.gd}
  \item Sub-interactables: \texttt{Channel1\,--\,3} (toggleable), \texttt{ConfirmFlow}
        (the water gate) with IDs \texttt{ep2.water\_flow.channel\_\{1,2,3\}}
        and \texttt{ep2.water\_flow.confirm}
  \item Action label: ``Open''\,/\,``Close'' (updated dynamically), ``Send Water'' for confirm
  \item Exports: \texttt{expected\_open : Array[StringName]} (default
        \texttt{[channel\_1, channel\_3]})
  \item Mechanic: toggling a channel flips its \texttt{is\_open} flag and the
        action label; confirming compares the set of open channels against
        \texttt{expected\_open} regardless of order.
  \item Solve condition: open-channel set equals \texttt{expected\_open} on confirm.
  \item Wrong-answer behavior: shows \texttt{ep2.water\_flow\_wrong} dialogue;
        channel states are preserved (no reset).
  \item Fragment reward: \texttt{ep2.compass.frag\_2}, MiniFrame slot 1.
\end{itemize}

\subsection{Mist Symbol (zone 3)}

\begin{itemize}[nosep]
  \item Scene: \texttt{episodes/episode\_2/puzzles/mist\_symbol/} \texttt{mist\_symbol\_puzzle.tscn}
  \item Script: same folder, \texttt{mist\_symbol\_puzzle.gd}
  \item Sub-interactables: \texttt{PanelA\,--\,D} with IDs
        \texttt{ep2.mist\_symbol.panel\_\{a,b,c,d\}}; a static
        \texttt{ReferenceSymbol} \texttt{Sprite2D} (deliberately not an
        \texttt{Interactable}; has no collision shape, so
        \texttt{InteractionManager} ignores it).
  \item Action label: ``Examine''
  \item Exports: \texttt{correct\_panel : StringName} (default
        \texttt{\&"ep2.mist\_symbol.panel\_c"})
  \item Mechanic: examining a panel compares its ID to \texttt{correct\_panel}.
  \item Solve condition: the examined panel ID equals \texttt{correct\_panel}.
  \item Wrong-answer behavior: shows \texttt{ep2.mist\_symbol\_wrong} dialogue;
        no state change.
  \item Fragment reward: \texttt{ep2.compass.frag\_3}, MiniFrame slot 2.
\end{itemize}

\subsection{Rock Water (zone 4)}

\begin{itemize}[nosep]
  \item Scene: \texttt{episodes/episode\_2/puzzles/rock\_water/} \texttt{rock\_water\_puzzle.tscn}
  \item Script: same folder, \texttt{rock\_water\_puzzle.gd}
  \item Sub-interactables: \texttt{MarkA\,--\,D} with IDs
        \texttt{ep2.rock\_water.mark\_\{a,b,c,d\}} positioned lowest-to-highest.
  \item Action label: ``Touch''
  \item Exports: \texttt{expected\_order : Array[StringName]} (default
        \texttt{[mark\_a, mark\_b, mark\_c, mark\_d]})
  \item Mechanic: each tap appends to \texttt{\_tapped\_sequence} and validates
        the prefix; if the prefix diverges, the sequence is cleared and
        \texttt{ep2.rock\_water\_wrong} dialogue plays.
  \item Solve condition: \texttt{\_tapped\_sequence} matches the full
        \texttt{expected\_order}.
  \item Wrong-answer behavior: sequence reset; dialogue shown; puzzle state
        remains ACTIVE.
  \item Fragment reward: \texttt{ep2.compass.frag\_4}, MiniFrame slot 3.
        Filling slot 3 triggers \texttt{key\_item\_completed(\&"key.mixed\_compass")}.
\end{itemize}

\subsection{Save/Load Implications}

For all four puzzles, \texttt{PuzzleBase.\_ready()} consults
\texttt{GameState.is\_puzzle\_completed(puzzle\_id)}. If completed on load,
\texttt{\_state} becomes \texttt{SOLVED}, \texttt{\_on\_already\_solved()} runs
(hiding sub-interactables), and the puzzle does not auto-start. Collected
fragments are restored to the MiniFrame via \texttt{\_restore\_from\_state()}.
A \texttt{FragmentPickup} whose fragment is already in
\texttt{GameState.collected\_fragments} stays hidden.

% ============================================================================
\section{Bridge Transition}

\subsection{Removal of PrototypeEndCard from the Bridge Scene}

Per P36, the \texttt{EndCardLayer} (\texttt{CanvasLayer}) and the
\texttt{PrototypeEndCard} node were removed from
\texttt{episodes/episode\_2\_bridge/zones/} \texttt{zone\_sunlit\_clearing.tscn}.
The \texttt{ui/prototype\_end\_card.tscn} and \texttt{.gd} files remain on
disk so that the Phase 1 reference flow can still be reproduced in isolated
tests, but they are no longer instanced in any zone.

\subsection{Live Transition via EpisodeController}

The bridge puzzle (\texttt{SunlitMapActivationPuzzle}, Phase 1) still emits
\texttt{key\_item\_used(\&"key.secret\_map\_card", \&"sunlit\_clearing")} on
solve. \texttt{EpisodeController} now listens for this signal:

\begin{lstlisting}
func _on_key_item_used(key_item_id: StringName, context: StringName) -> void:
    if key_item_id == Constants.KEY_SECRET_MAP_CARD \
            and context == &"sunlit_clearing":
        var path := zone_path_for_id(Constants.ZONE_EP2_1)
        if path.is_empty():
            push_error("EpisodeController: ep2.zone_1 path not registered.")
            return
        EventBus.zone_change_requested.emit(path)
\end{lstlisting}

\texttt{\_change\_scene\_faded} then runs its standard
\texttt{SoftTransition} play-out, \texttt{change\_scene\_to\_file}, and
play-in. Scene changes remain centralized in \texttt{EpisodeController}; no
other module calls \texttt{change\_scene\_to\_file}.

% ============================================================================
\section{Mixed Compass Completion and End Card}

\subsection{Fragment Collection Chain}

Each ep2 puzzle solve fires \texttt{fragment\_revealed(puzzle\_id, fragment\_id)}.
The zone's \texttt{FragmentPickup} reacts by un-hiding itself. The player
taps it and presses ``Collect'', which causes \texttt{FragmentPickup.\_collect()}
to:

\begin{enumerate}[nosep]
  \item mark the fragment collected on \texttt{GameState};
  \item emit \texttt{fragment\_collected(fragment\_id, key\_item\_id)};
  \item emit \texttt{save\_requested(\&"fragment\_collected")};
  \item call \texttt{queue\_free()}.
\end{enumerate}

\texttt{MiniFrame} listens to \texttt{fragment\_collected}, looks up the
\texttt{frame\_slot} for the fragment by scanning the active episode's
definitions folder, and animates the slot fill. After filling slot 3 (the
fourth compass fragment), \texttt{\_check\_completion()} sees four filled
slots and emits \texttt{key\_item\_completed(\&"key.mixed\_compass")}.

\subsection{Ep2EndCard}

\texttt{ui/ep2\_end\_card.gd} (a \texttt{Control}) is hidden on
\texttt{\_ready()} and connects to \texttt{EventBus.key\_item\_completed}.
On the first matching event (the guard
\texttt{key\_item\_id != \&"key.mixed\_compass"} filters out the Secret Map
Card), the handler:

\begin{enumerate}[nosep]
  \item disconnects so that subsequent events do not re-show the card;
  \item waits 2.5\,s for the solved dialogue to clear;
  \item emits \texttt{ep2.compass\_completed} via \texttt{dialogue\_requested};
  \item fades the card in over 0.8\,s.
\end{enumerate}

The end card displays the Orange fictional line ``RUUU!'' and the English
line ``The compass is ready. The river awaits. To be continued.''.
A ``Play Again'' button opens a confirmation panel with ``Yes, again'' and
``No, stay'' choices.

\subsection{Play Again --- Save Wipe and Reset}

``Yes, again'' calls \texttt{SaveSystem.wipe()} (which deletes
\texttt{user://save.json} if present and calls \texttt{GameState.reset()}),
plays a soft transition out, and emits
\texttt{zone\_change\_requested(ep1.zone\_1)}. \texttt{EpisodeController}
performs the scene change, and the player re-enters Episode 1 with an empty
save. ``No, stay'' simply hides the confirmation panel; the end card remains.

\texttt{Ep2EndCard} routes its scene change through
\texttt{EventBus.zone\_change\_requested.emit(\dots)} and never calls
\texttt{change\_scene\_to\_file} directly --- consistent with the C05
architectural rule.

% ============================================================================
\section{Final Post-Audit Fixes}

The Phase 2 audit identified four defects. All four have been resolved on
\texttt{main} with one commit each.

\begin{center}
\begin{longtable}{p{0.06\linewidth} p{0.24\linewidth} p{0.32\linewidth} p{0.20\linewidth} p{0.07\linewidth}}
\toprule
\textbf{ID} & \textbf{Problem} & \textbf{Fix} & \textbf{Commit} & \textbf{Result} \\
\midrule
\endfirsthead
\bottomrule
\endlastfoot

BUG-001 &
\texttt{FragmentPickup} nodes were missing from all four Episode 2 zones. Puzzle solves fired \texttt{fragment\_revealed} but nothing in the scene responded; fragments never appeared and the entire reward chain broke. &
Added a \texttt{FragmentPickup} under \texttt{Interactables} in each of the four ep2 zones, each with an inline \texttt{FragmentReward} sub-resource and an explicit \texttt{action\_dispatched} signal connection. .tscn-only change. &
\texttt{cc5a873} \newline \texttt{fix(ep2): add FragmentPickup nodes to all four Episode 2 zones (BUG-001)} &
\sevFixed \\

BUG-002 &
Each ep2 puzzle called \texttt{start\_puzzle()} synchronously in its own \texttt{\_ready()}. Because the puzzle node lives in \texttt{Interactables} (an earlier sibling than \texttt{HintButton} and \texttt{DialogueBox} in the zone tree), \texttt{puzzle\_started} and \texttt{dialogue\_requested} fired before those listeners connected. The hint button stayed disabled and the intro dialogue was missed. &
Each puzzle's \texttt{\_ready()} now uses \texttt{call\_deferred("\_deferred\_start")}; \texttt{\_deferred\_start()} re-checks \texttt{State.INACTIVE} before invoking \texttt{start\_puzzle()} and then \texttt{\_connect\_manager()}. \texttt{PuzzleBase} is unchanged. &
\texttt{88d520f} \newline \texttt{fix(ep2): defer puzzle auto-start so HintButton/DialogueBox can hear puzzle\_started (BUG-002)} &
\sevFixed \\

BUG-003 &
\texttt{ui/prototype\_end\_card.gd} called \texttt{get\_tree().change\_scene\_to\_file()} directly from its restart handler, violating the C05 contract that only \texttt{EpisodeController} performs scene changes. The card is no longer instanced in the bridge zone, but the contract violation remained on disk. &
Replaced the direct call with \texttt{EventBus.zone\_change\_requested.emit(zone1\_path)}. The existing \texttt{SoftTransition} play-out is preserved. &
\texttt{28283a3} \newline \texttt{fix(arch): route prototype\_end\_card restart through EpisodeController (BUG-003)} &
\sevFixed \\

BUG-004 &
\texttt{data/dialogue/episode\_2.json} held a non-canonical English line for \texttt{ep2.compass\_completed} (``The compass is whole. The river is waiting.''), diverging from \texttt{phase2\_prompts.md} \S10.1. &
Restored the canonical text: ``The Mixed Compass is complete. It will guide me wherever I need to go.''. JSON remains valid. &
\texttt{dfa3251} \newline \texttt{fix(data): restore canonical ep2.compass\_completed dialogue text (BUG-004)} &
\sevFixed \\

\end{longtable}
\end{center}

\subsection{Verification Method}

Each fix was verified by static inspection of the current repository:

\begin{itemize}[nosep]
  \item \textbf{BUG-001}: Confirmed each of the four zone scenes contains a
        \texttt{FragmentPickup} node under \texttt{Interactables}, an inline
        \texttt{Resource\_reward} sub-resource with the correct
        \texttt{fragment\_id}, \texttt{key\_item\_id}, and \texttt{frame\_slot}
        (0/1/2/3 for zones 1/2/3/4), and an
        \texttt{[connection signal="action\_dispatched"\dots]} entry. Zone 4
        additionally retains \texttt{CompletionTrigger},
        \texttt{Ep2CompletionLayer}, and \texttt{Ep2EndCard}.
  \item \textbf{BUG-002}: Confirmed all four ep2 puzzle scripts (Sun
        Reflection, Water Flow Path, Mist Symbol, Rock Water) call
        \texttt{super()} first, then defer the start via
        \texttt{call\_deferred("\_deferred\_start")}, and that
        \texttt{\_deferred\_start} guards against state mutation between the
        deferral and execution.
  \item \textbf{BUG-003}: Confirmed \texttt{grep "change\_scene\_to\_file"
        ui/prototype\_end\_card.gd} returns no matches; the only remaining
        occurrence of \texttt{change\_scene\_to\_file} in the repository is in
        \texttt{globals/episode\_controller.gd}, the sole authorized caller.
  \item \textbf{BUG-004}: Confirmed line 15 of
        \texttt{data/dialogue/episode\_2.json} contains exactly the canonical
        English string. JSON parse is valid.
\end{itemize}

% ============================================================================
\section{Save / Load Behavior}

Phase 2 preserves the Phase 1 save contract.

\begin{itemize}[nosep]
  \item \textbf{Save trigger}: a save is requested only via
        \texttt{EventBus.save\_requested}. In Episode 2 the only emitter is
        \texttt{FragmentPickup.\_collect()}, fired after each of the four
        compass fragments is collected.
  \item \textbf{Debounce}: \texttt{SaveSystem} uses a \texttt{\_save\_queued}
        flag with \texttt{call\_deferred} to coalesce same-frame requests
        into a single write. No per-frame saves.
  \item \textbf{Persisted state}: \texttt{completed\_puzzles},
        \texttt{collected\_fragments}, \texttt{owned\_key\_items},
        \texttt{completed\_key\_items}, \texttt{flags},
        \texttt{current\_episode}, and \texttt{current\_zone}. The schema
        version (1) is unchanged.
  \item \textbf{MiniFrame restore}: on zone load,
        \texttt{MiniFrame.set\_key\_item(\dots)} calls
        \texttt{\_restore\_from\_state()}, which fills slots for any compass
        fragments already in \texttt{GameState.collected\_fragments} using
        \texttt{\_fill\_slot\_instant} (no animation, no re-emit of
        \texttt{key\_item\_completed}).
  \item \textbf{Already-solved puzzles}: \texttt{PuzzleBase.\_ready()}
        detects \texttt{is\_puzzle\_completed(puzzle\_id)} and transitions
        directly to \texttt{State.SOLVED}, skipping auto-start and hiding
        sub-interactables via \texttt{\_on\_already\_solved()}.
  \item \textbf{Play Again}: \texttt{SaveSystem.wipe()} removes
        \texttt{user://save.json} if it exists (with
        \texttt{FileAccess.file\_exists} guard) and calls
        \texttt{GameState.reset()}. The wipe is safe when no save file is
        present.
\end{itemize}

% ============================================================================
\section{Phase 1 Non-Regression Notes}

Phase 2 was implemented through additive prompts and surgical edits. The
following Phase 1 behaviors remain intact:

\begin{itemize}[nosep]
  \item \textbf{Episode 1 zones and puzzles}: untouched. The four ep1 puzzle
        scenes, the four ep1 puzzle scripts, and the four ep1 zone scenes
        carry no Phase 2 modifications.
  \item \textbf{Secret Map Card flow}: zones 2\,--\,4 still place a
        \texttt{FragmentPickup} for the corresponding map fragment; the
        \texttt{MapCompletionTrigger} in zone 4 still routes through the
        bridge zone via \texttt{EventBus.zone\_change\_requested}.
  \item \textbf{Bridge zone ending}: intentionally changed. The bridge no
        longer shows \texttt{PrototypeEndCard}; instead, solving the bridge
        puzzle transitions to \texttt{ep2.zone\_1} through
        \texttt{EpisodeController}.
  \item \textbf{PrototypeEndCard module}: still present on disk
        (\texttt{ui/prototype\_end\_card.tscn} and \texttt{.gd}). After the
        BUG-003 fix it no longer violates C05 and remains available for
        isolated Phase 1 reference tests.
  \item \textbf{Episode 1 MiniFrame}: still binds to
        \texttt{secret\_map\_card.tres} when an ep1 zone loads, courtesy of
        the unchanged \texttt{EpisodeController.\_EPISODE\_KEY\_ITEMS} entry.
\end{itemize}

% ============================================================================
\section{Manual QA Status}

Most QA work for Phase 2 was completed prior to this report (P31\,--\,P42
prompt verification, the dedicated Phase 2 audit, and the four post-audit
fixes).

\subsection{Completed}

\begin{itemize}[nosep]
  \item Static implementation review of all P31\,--\,P42 deliverables.
  \item Phase 2 audit (\texttt{phase2\_testprompt.md}).
  \item Fix prompts FX2-009 through FX2-012 applied, committed, and
        statically verified in the current repository.
\end{itemize}

\subsection{Recommended Final Smoke Test}

Before tagging a release candidate, perform a single end-to-end runtime
playthrough from an empty save:

\begin{enumerate}[nosep]
  \item Delete \texttt{user://save.json}.
  \item Play through Episode 1 (zones 1\,--\,4), collect all four Secret Map
        Card fragments, and observe the map completion celebration into the
        bridge zone.
  \item Solve the Sunlit Map Activation bridge puzzle; verify the soft fade
        transitions into \texttt{ep2.zone\_1} (and not \texttt{PrototypeEndCard}).
  \item In each ep2 zone: verify the puzzle auto-start triggers the intro
        dialogue line and that the \texttt{HintButton} is active and shows
        the correct one-level hint.
  \item Solve each ep2 puzzle, collect the resulting compass fragment, and
        verify that the corresponding MiniFrame slot fills and that a save
        is written.
  \item After collecting frag\_4, verify the Mixed Compass completion
        dialogue and the \texttt{Ep2EndCard} fade-in.
  \item Press ``Play Again'' $\to$ ``Yes, again'' and verify the save is
        wiped and the prototype resets to \texttt{ep1.zone\_1} with an empty
        MiniFrame.
  \item Run a web export and repeat steps 2\,--\,7 in the browser build to
        validate audio gating, touch input, and HUD scaling.
\end{enumerate}

% ============================================================================
\section{Known Limitations}

The following are real limitations visible from the current implementation.
They are not blocking defects.

\begin{itemize}
  \item \textbf{Placeholder fragment art}: the four compass fragments declare
        \texttt{art\_path = "res://art/compass\_frag\_\{1,2,3,4\}.png"}. If
        those files are not yet present, the MiniFrame slot fill uses the
        empty-slot fallback. Replace with final art before release.
  \item \textbf{Static verification only}: this report is based on static
        inspection of the repository. A runtime playthrough and a web export
        smoke test (see Section~14.2) are still recommended.
  \item \textbf{Puzzle scene visuals are placeholder}: the puzzle sub-interactables
        are colored \texttt{Sprite2D}s with \texttt{RectangleShape2D} hit boxes,
        sufficient for mechanic verification but not for final art delivery.
\end{itemize}

% ============================================================================
\section{Conclusion}

\subsection{Phase 2 Status}

The \textit{Orange} Phase 2 implementation is complete. Prompts P31\,--\,P42
deliver Episode 2 in full: four zones, four puzzles, four Mixed Compass
fragments, the Mixed Compass completion moment, and the Episode 2 end card.
The bridge transition has been migrated from the Phase 1 prototype end card
to a live \texttt{EpisodeController}-owned scene change.

\subsection{Audit Status}

The Phase 2 audit identified four defects --- two critical, one medium, one
low. All four were fixed in single-purpose commits
(\texttt{cc5a873}, \texttt{88d520f}, \texttt{28283a3}, \texttt{dfa3251})
and verified statically.

\subsection{Architectural Integrity}

Phase 2 introduces no new autoloads, no new global signals, and no new
folders outside the additions specified in \texttt{phase2\_prompts.md} \S5.
\texttt{EpisodeController} remains the sole owner of
\texttt{change\_scene\_to\_file}. \texttt{SaveSystem} remains the sole writer
of \texttt{user://save.json}. The Phase 1 architecture is preserved end to end.

\subsection{Final Verdict}

\begin{center}
  \large\bfseries\color{passgre}
  Orange Phase 2 --- PASS (pending runtime smoke test)
\end{center}

\begin{center}
  \normalsize Episode 2 implemented across P31\,--\,P42.\\
  All four post-audit fixes verified.\\
  Ready for runtime playthrough and web export validation.
\end{center}

% ============================================================================
\appendix
\section{Fix Prompt Reference}

\begin{center}
\begin{tabular}{lllll}
\toprule
\textbf{Bug} & \textbf{Severity} & \textbf{Fix Prompt} & \textbf{Commit} & \textbf{Status} \\
\midrule
BUG-001 & \sevCrit & FX2-009 & \texttt{cc5a873} & \sevFixed \\
BUG-002 & \sevCrit & FX2-010 & \texttt{88d520f} & \sevFixed \\
BUG-003 & \sevMed  & FX2-011 & \texttt{28283a3} & \sevFixed \\
BUG-004 & \sevLow  & FX2-012 & \texttt{dfa3251} & \sevFixed \\
\bottomrule
\end{tabular}
\end{center}

\section{File Inventory Summary (Phase 2 additions)}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Category} & \textbf{Count} \\
\midrule
Episode 2 zone scenes (\texttt{.tscn})         & 4 \\
Episode 2 puzzle scenes (\texttt{.tscn})       & 4 \\
Episode 2 puzzle scripts (\texttt{.gd})        & 4 \\
Episode 2 puzzle definitions (\texttt{.tres})  & 4 \\
Episode 2 JSON data files                      & 3 \\
End card scene (\texttt{.tscn})                & 1 \\
End card script (\texttt{.gd})                 & 1 \\
\midrule
\textbf{Files edited (surgical)} &  \\
\quad \texttt{globals/constants.gd}                                       & + ep2 constants \\
\quad \texttt{globals/episode\_controller.gd}                             & + ep2 routes, key\_item\_used handler \\
\quad \texttt{episodes/zone.gd}                                           & + ep2 prefix detection \\
\quad \texttt{ui/hint\_button.gd}                                         & + ep2 hints path \\
\quad \texttt{ui/dialogue\_box.gd}                                        & + ep2 dialogue path \\
\quad \texttt{interaction/interaction\_manager.gd}                        & + ep2 labels path \\
\quad \texttt{episodes/episode\_2\_bridge/zones/zone\_sunlit\_clearing.tscn} & - EndCardLayer, - PrototypeEndCard \\
\quad \texttt{ui/prototype\_end\_card.gd}                                 & C05 compliance (BUG-003) \\
\quad \texttt{data/dialogue/episode\_2.json}                              & canonical text (BUG-004) \\
\bottomrule
\end{tabular}
\end{center}

\end{document}
